Fluent statistical computing interfaces for biological data analysis

### 2020-07-15 Rmd/04-intron.Rmd
add extra references

FASTQ files were aligned to the GRCz11 reference genome using subjunc with
the default parameters called from Rsubread to produce BAM files for each
sample. The coverage was then estimated directly from the set of BAM files
using **superintronic** into the long form *GRanges* representation we described above.

>>>>

FASTQ files were aligned to the GRCz11 reference genome using subjunc with
the default parameters called from Rsubread to produce BAM files for each
sample [@Liao2013; @Liao2019-qn]. The coverage was then estimated directly from the set of BAM files
using **superintronic** into the long form *GRanges* representation we described above.
